Reading text files

### 2024-08-04 text/20/reading-text-files.Rmd
Removed brackets from generic code chunks

```{}
![A non-text file displayed in notepad](../../../web/images/reading-text-files01.png)
```

@@

```{}
![Data set on movies](../../../web/images/read-text-files03.png)
```

@@

```{}
![Data dictionary](../../../web/images/read-text-files06.png)
```

@@

```{}
![Example of a space delimited file](../../../web/images/read-text-files02.png)
```

@@

```{}
![Dataset showing COVID-19 deaths over time](../../../web/images/read-text-files04.png)
```

@@

```{}
![Dataset of revenues for selected movies](../../../web/images/read-text-files05.png)
```

>>>>

```
![A non-text file displayed in notepad](../../../web/images/reading-text-files01.png)
```

@@

```
![Data set on movies](../../../web/images/read-text-files03.png)
```

@@

```
![Data dictionary](../../../web/images/read-text-files06.png)
```

@@

```
![Example of a space delimited file](../../../web/images/read-text-files02.png)
```

@@

```
![Dataset showing COVID-19 deaths over time](../../../web/images/read-text-files04.png)
```

@@

```
![Dataset of revenues for selected movies](../../../web/images/read-text-files05.png)
```
